Modelling Weddell Sea Food Web

### 2022-06-13 ModellingWeddellSea.Rmd
Add sources to interaction calculation

#
# Calculate interaction intensity
#
wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )

>>>>

#
# Calculate interaction intensity
#
wedd_df <- wedd_df %>% mutate(res_mass_mean = res_mass_mean*1000,con_mass_mean = con_mass_mean*1000)
wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )
